Tables and Figures

### 2022-09-29 paper/results.Rmd
results first draft

```{r setup, include = FALSE}
knitr::opts_chunk$set(
 echo = FALSE,
 message = FALSE,
 warning = FALSE,
 fig.width = 7,
 fig.height = 4, 
 dpi = 300
)

@@

__Table 1__ Participant characteristics

@@

tbl_gtsummary <- tbl_summary_design %>% 
 tbl_svysummary(
  by = svy_year,
  include = c(nobs, 
              starts_with("demo"),
              starts_with('bp'), 
              starts_with('htn'),
              starts_with('cc')),
  missing = 'no',
  label = list(nobs ~ "No. of Adults"),
  statistic = list(
   all_categorical() ~ "{p}",
   all_continuous() ~ "{mean} ({sd})",
   nobs ~ "{N_unweighted}"
  )
 ) %>%
 modify_header(all_stat_cols() ~ "**{level}**") %>%
 modify_footnote(all_stat_cols() ~ NA)

as_flex_table(tbl_gtsummary) %>% 
 theme_box() %>% 
 width(width = 0.90) %>% 
 width(j = 1, width = 2) %>% 
 align(align = 'center') %>% 
 align(j = 1, align = 'left')

@@

__Figure 1__ Prevalence of hypertension by calendar year

@@

__Figure 2__ Antihypertensive medication use by calendar year among adults with hypertension

@@

__Figure 3__ Prevalence of resistant hypertension among adults with hypertension taking antihypertensive medication

@@

nhanes_visualize(
 outcome = 'htn_resistant_accaha', 
 subset_variables = c(subset_variables, 'htn_accaha', 'bp_med_use'),
 subset_values = c(subset_values, 'Yes', 'Yes'),
 years = 'all'
)[[1]] %>% 
 layout(font = list(size = 40))

@@

__Figure S1__: Participants included in the current analysis

@@

__Figure S2__ Prevalence of hypertension by age group

@@

__Figure S3__ Prevalence of hypertension by sex

@@

__Figure S4__ Prevalence of hypertension by race/ethnicity

@@

>>>>

```{r setup, include = FALSE}

knitr::opts_chunk$set(
 echo = FALSE,
 message = FALSE,
 warning = FALSE,
 fig.width = 7,
 fig.height = 4, 
 dpi = 300
)

@@

**RESULTS**

A total of `r sum(nhanes_bp$svy_subpop_htn)` survey participants (mean age 46 years, 52% women, 68% non-Hispanic white) were included in the BP and hypertension cohort (**Table 1**). The estimated prevalence of hypertension was 45.9% (95% CI 43.1, 48.8) in 1999-2000, 43.8% (95% CI 41.1, 46.5) in 2009-2010, and 47.0% (95% CI 44.5, 49.5) in 2017-2020 (**Figure 1**). For US adults in 2017-2020, hypertension was estimated to be more prevalent among older versus younger adults (**Figure S2**), more prevalent among men versus women (**Figure S3**), and more prevalent among adults are non-Hispanic Black versus other race/ethnicity subgroups (**Figure S4**).

**Self-reported antihypertensive medication use**

Among US adults with hypertension, the estimated percentage who self-reported using antihypertensive medication was 35.0% (95% CI 30.7, 39.7) in 1999-2000, 52.8% (95% CI 48.3, 57.2) in 2009-2010, and 51.3% (95% CI 48.7, 54.0) in 2017-2020 (**Figure 2**). For US adults with hypertension in 2017-2020, adults aged 65 to 74 years had a higher estimated percentage who self-report using antihypertensive medication versus other age groups (**Figure S5**), women had a higher estimated percentage who self-report using antihypertensive medication compared to men (**Figure S6**), and Hispanic adults had a lower estimated percentage who self-report using antihypertensive medication versus other race/ethnicity subgroups (**Figure S7**).

**Classes of antihypertensive medication**

Among US adults with hypertension, the estimated percentage using one or more classes of antihypertensive medication was 38.5% (95% CI 34.5, 42.4) in 1999-2000, 54.3% (95% CI 50.1, 58.5) in 2009-2010, and 55.4% (95% CI 54.0, 57.8) in 2017-2020 (**Figure 3**). For US adults with hypertension in 2017-2020, adults aged 75+ had a higher estimated percentage using one or more antihypertensive medication class versus other age groups (**Figure S8**), women a higher estimated percentage using one or more antihypertensive medication class versus men (**Figure S9**), and non-Hispanic white adults a higher estimated percentage using one or more classes of antihypertensive medication versus other race/ethnicity groups (**Figure S10**).

**Resistant hypertension**

Among US adults with hypertension using three or more classes of antihypertensive medication, the estimated prevalence of resistant hypertension was 70.6 (95% CI 62.8, 78.3) in 1999-2000, 62.7 (95% CI 58.6, 66.7) in 2009-2010, and 66.0 (95% CI 61.9, 70.1) in 2017-2020 (**Figure 4**). For US adults with hypertension using three or more classes of antihypertensive medication in 2017-2020, adults aged 18 to 44 years had a higher estimated prevalence of resistant hypertension versus other age groups (**Figure S11**), men a higher estimated prevalence versus women (**Figure S12**), and non-Hispanic Black adults a higher estimated prevalence versus other race/ethnicity groups (**Figure S13**).

```{r}
block_section(
  prop_section(
    page_size = page_size(orient = "portrait"),
    type = "continuous"
  )
)
```

__Table 1__ Characteristics of participants included in the blood pressure and hypertension cohort of the online platform.

@@

tbl_gtsummary <- tbl_summary_design %>% 
 tbl_svysummary(
  by = svy_year,
  include = c(nobs, 
              starts_with("demo"),
              starts_with('bp'),
              starts_with('htn'),
              starts_with('cc')),
  missing = 'no',
  label = list(nobs ~ "No. of Adults"),
  statistic = list(
   all_categorical() ~ "{p}",
   all_continuous() ~ "{mean} ({sd})",
   nobs ~ "{N_unweighted}"
  )
 ) %>%
 modify_header(all_stat_cols() ~ "**{level}**") %>%
 add_overall(last = FALSE, col_label = "**Overall**") %>% 
 modify_footnote(all_stat_cols() ~ NA)

as_flex_table(tbl_gtsummary) %>% 
 theme_box() %>% 
 width(width = 0.8) %>% 
 width(j = 1, width = 2) %>% 
 align(align = 'center') %>% 
 align(j = 1, align = 'left')

@@

__Figure 1__ Prevalence of hypertension by calendar year.

@@

__Figure 2__ Antihypertensive medication use by calendar year among adults with hypertension.

@@

__Figure 3__ Number of antihypertensive medication classes by calendar period among adults with hypertension.

@@

nhanes_visualize(
 outcome = 'bp_med_n_class', 
 subset_variables = c(subset_variables, 'htn_accaha'),
 subset_values = c(subset_values, 'Yes'),
 years = 'all'
)[[1]] %>% 
 layout(font = list(size = 40))

@@

__Figure 4__ Prevalence of resistant hypertension among adults with hypertension taking three or more classes of antihypertensive medication.

nhanes_visualize(
 outcome = 'htn_resistant_accaha',
 subset_variables = c(subset_variables, 
                      'htn_accaha', 
                      'bp_med_n_class'),
 subset_values = c(subset_values, 
                   'Yes', 
                   list(c('Three', 'Four or more'))),
 years = 'all'
)[[1]] %>%
 layout(font = list(size = 40))

@@

__Figure S1__: Participants included in the current analysis.

__Figure S2__ Prevalence of hypertension by age group in 2017-2020.

@@

__Figure S3__ Prevalence of hypertension by sex in 2017-2020.

@@

__Figure S4__ Prevalence of hypertension by race/ethnicity in 2017-2020.

@@

__Figure S5__ Antihypertensive medication use by age category in 2017-2020 among adults with hypertension.

nhanes_visualize(
 outcome = 'bp_med_use', 
 exposure = 'demo_age_cat',
 subset_variables = c(subset_variables, 'htn_accaha'),
 subset_values = c(subset_values, 'Yes'),
 years = 'most_recent'
)[[1]] %>% 
 layout(font = list(size = 40))

__Figure S6__ Antihypertensive medication use by sex in 2017-2020 among adults with hypertension.

nhanes_visualize(
 outcome = 'bp_med_use', 
 exposure = 'demo_gender',
 subset_variables = c(subset_variables, 'htn_accaha'),
 subset_values = c(subset_values, 'Yes'),
 years = 'most_recent'
)[[1]] %>% 
 layout(font = list(size = 40))

__Figure S7__ Antihypertensive medication use by race/ethnicity in 2017-2020 among adults with hypertension.

nhanes_visualize(
 outcome = 'bp_med_use', 
 exposure = 'demo_race',
 subset_variables = c(subset_variables, 'htn_accaha'),
 subset_values = c(subset_values, 'Yes'),
 years = 'most_recent'
)[[1]] %>% 
 layout(font = list(size = 40))

__Figure S8__ Number of antihypertensive medication classes by age category in 2017-2020 among adults with hypertension.

```{r, fig.height = 5}

margin <- list(l = 50, r = 50, b = 50, t = 300)

nhanes_visualize(
 outcome = 'bp_med_n_class', 
 exposure = 'demo_age_cat',
 subset_variables = c(subset_variables, 'htn_accaha'),
 subset_values = c(subset_values, 'Yes'),
 years = 'most_recent',
 pool = TRUE
)[[1]] %>% 
 layout(font = list(size = 40), margin = margin)

__Figure S9__ Number of antihypertensive medication classes by sex in 2017-2020 among adults with hypertension.

```{r, fig.height = 5}

nhanes_visualize(
 outcome = 'bp_med_n_class', 
 exposure = 'demo_gender',
 subset_variables = c(subset_variables, 'htn_accaha'),
 subset_values = c(subset_values, 'Yes'),
 years = 'most_recent',
 pool = TRUE
)[[1]] %>% 
 layout(font = list(size = 40), margin = margin)

__Figure S10__ Number of antihypertensive medication classes by race/ethnicity in 2017-2020 among adults with hypertension.

```{r, fig.height = 5}

nhanes_visualize(
 outcome = 'bp_med_n_class', 
 exposure = 'demo_race',
 subset_variables = c(subset_variables, 'htn_accaha'),
 subset_values = c(subset_values, 'Yes'),
 years = 'most_recent',
 pool = TRUE
)[[1]] %>% 
 layout(font = list(size = 40), margin = margin)

__Figure S11__ Prevalence of resistant hypertension by age category in 2017-2020 among adults with hypertension taking three or more classes of antihypertensive medication.

nhanes_visualize(
 outcome = 'htn_resistant_accaha',
 exposure = 'demo_age_cat',
 subset_variables = c(subset_variables, 
                      'htn_accaha', 
                      'bp_med_n_class'),
 subset_values = c(subset_values, 
                   'Yes', 
                   list(c('Three', 'Four or more'))),
 years = 'most_recent'
)[[1]] %>%
 layout(font = list(size = 40))

__Figure S12__ Prevalence of resistant hypertension by sex in 2017-2020 among adults with hypertension taking three or more classes of antihypertensive medication.

nhanes_visualize(
 outcome = 'htn_resistant_accaha',
 exposure = 'demo_gender',
 subset_variables = c(subset_variables, 
                      'htn_accaha', 
                      'bp_med_n_class'),
 subset_values = c(subset_values, 
                   'Yes', 
                   list(c('Three', 'Four or more'))),
 years = 'most_recent'
)[[1]] %>%
 layout(font = list(size = 40))

__Figure S13__ Prevalence of resistant hypertension by race/ethnicity in 2017-2020 among adults with hypertension taking three or more classes of antihypertensive medication.

nhanes_visualize(
 outcome = 'htn_resistant_accaha',
 exposure = 'demo_race',
 subset_variables = c(subset_variables, 
                      'htn_accaha', 
                      'bp_med_n_class'),
 subset_values = c(subset_values, 
                   'Yes', 
                   list(c('Three', 'Four or more'))),
 years = 'most_recent'
)[[1]] %>%
 layout(font = list(size = 40))
